
\section{Extracurricular Activities}

\denseouterlist{

\entrymid[\textbullet]
{Honors Program Committee}{2020\textendash Current}
{Chair of the committee.\\ Meet monthly to review policies and procedures of the Honors Program. Responsible for reviewing new curriculum and assessing the honors program.}

\entrymid[\textbullet]
{Teacher Education Committee}{2020\textendash Current}
{Meet monthly to review policies and procedures of the education program along with student teacher candidates at Peru State College.}

\entrymid[\textbullet]
{Worship Leader}{2017\textendash Current}
{Assist with and lead worship at Calvary Christian Center every Sunday.}

\entrymid[\textbullet]
{Assessment Committee}{2018\textendash2020}
{Committee meets biweekly to fulfill the responsibility of assessing of courses and academic programs at Peru State College.}

\entrymid[\textbullet]
{Honors Program Work Group}{2018\textendash2019}
{Met biweekly to rewrite the Honors Program at Peru State College.}

\entrymid[\textbullet]
{Member of Alpha Mu Omega (PSC Math Club)}{2010\textendash 2014}
{President for 2 years: Was responsible for leading meetings, recruiting new members, and assisting with the organization of and running of the Annual Mathematics Challenge.\\
Treasurer for 1 year: Was responsible for handling money for the club.}

\entrymid[\textbullet]
{Member of Campus Crusade for Christ}{2010\textendash 2014}
{Attended conferences and helped to host weekly meetings on campus. \\Participated in the worship band.}


}
